\input{common_preamble}
\pagestyle{empty}
\usepackage{enumitem}

\begin{document}

\begin{center}
   {\Large
    \vspace{0.5em} % Adjust space before the title
    \textbf{\input{title}}%
    \par % Ends the paragraph here, which is important for the line break
   }
   \vspace{1.5em} % Adjust space after the title
   By Seyed Shayan Sajjadinia
\end{center}

\paragraph{Abstract.} \input{abstract}

\pagebreak

\begin{center}
   \textbf{\Large List of Activities during PhD Studies}\\
\end{center}

\begin{enumerate}[leftmargin=*]
    \item Performing a PhD project and disseminating results, as detailed at the beginning of the PhD dissertation and summarized as follows:
    \begin{itemize}
        \item Publication of two peer-reviewed papers at top journals (ranked Q1 when published), with another manuscript currently under review.
        \item Publication of one peer-reviewed conference proceedings paper, along with another recently accepted conference paper.
        \item Presentation of four conference abstracts (half presented through posters and the other half through oral presentations).
        \item Contributed an invited chapter to a forth-coming Wiley book.
        \item Open-sourcing most of the research code, such as the Python scripts and Fortran subroutines, with detailed documentation.
    \end{itemize}
    \item Participation in educational training programs, including:
    \begin{itemize}
        \item Two PhD courses focusing on research methods.
        \item Two technical courses in machine learning.
        \item One course on academic writing in English.
        \item Three summer schools: one in biomechanics (including a short oral presentation), and two others in \textit{in silico} medicine and advanced data science.
        \item One seminar on knowledge representation (including a short oral presentation).
    \end{itemize}
    \item Involvement in volunteer activities such as:
    \begin{itemize}
        \item Serving as a teaching assistant for an undergraduate mathematics course.
        \item Peer reviewing for top journals, as listed at \href{https://orcid.org/0000-0002-0789-6394}{orcid.org/0000-0002-0789-6394}.
    \end{itemize}
    \item Other activities:
    \begin{itemize}
        \item Reporting a mandatory and extensive literature review.
        \item Networking and collaborating with an international team of researchers.
        \item Attending yearly exams and presentations for project readers.
        \item Periodically presenting written and verbal updates of work to the supervisor.
        \item Self-learning research-related topics, such as graph neural networks.
        \item Attending general C1 English and A1-B1 Italian courses.
        \item Presenting a poster at a faculty evaluation meeting (invited by the faculty as one of the top five PhD students).
    \end{itemize}
\end{enumerate}

\end{document}
